---
title: "Erquaker package"
author: "Kirill Efremov"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Erquaker
This package contains functions for cleaning raw NOAA' significant earthquakes dataset
eq_clean_data(raw). Raw is a data.frame which contains DATE, YEAR, MONTH, DAY, LATITUDE, LONGITUDE,
TOTAL_DEATHS,EQ_PRIMARY,LOCATION_NAME varaibles.
Dataset can be obtained from  \href{https://www.ngdc.noaa.gov/nndc/struts/form?t=101650&s=1&d=1}{NOAA's}
```{r}
  library(readr)
  library(dplyr)
  library(magrittr)
  dataset_noaa_raw %>%
  eq_clean_data()%>%head()
```

Also for futher labeling of points we need trim LOCATION_NAME variable with eq_location_clean() function
```{r}
d<-dataset_noaa_raw %>%
  eq_clean_data()%>%eq_location_clean()
head(d)
```

# Now we can plot some information via geom_timeline function
```{r}
p<-d%>%subset(COUNTRY=="USA" | COUNTRY=="CHINA")%>%subset(DATE>=as.Date("2000-01-01"))%>%
   ggplot(aes(DATE, COUNTRY, colour = DEATHS, size = EQ_PRIMARY, label = LOCATION_NAME)) +
   geom_timeline()+
   guides(size = guide_legend("Richter scale value")) +
   guides(colour = guide_colorbar("# Deaths", label.theme = element_text(angle = 45, size = 8 ))) +
   ylab("") +
   theme_classic() +
   theme(legend.position="bottom", axis.line.y = element_blank())
p
```

Also we can add labels for circle points with names of places where events happened. And n_max is how much biggest event to mark

```{r}

p+geom_timeline_label(n_max=5)
```

The next step is mapping events with leaflet and eq_map() function
```{r}
dataset_noaa_raw %>%
 eq_clean_data() %>%
   dplyr::filter(COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000) %>%
   eq_map()
   # For Date annotation popup
   # eq_map(annot_col="DATE")
```

